---
title: "Logging Unapproved Package and Function Use"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Logging Unapproved Package and Function Use}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(logrx)
```

# 1. Create a named list
The named list contains the functions approved for use for each package. If all 
functions for a package are approved for use, list "All".

```{r}
approved_pkgs <- list(base = "mean",
                      dplyr = "All")
approved_pkgs
```

# 2. Build `approved.rds`
Pass the named list through `build_approved()` to build your tibble. We create 
a temp directory to save this for illustration.

```{r}
build_approved(approved_pkgs)
```

# 3. Save as `approved.rds`
You can use the `file` argument in `build_approved()` to save `approved.rds` 
instead of returning the tibble.

```{r}
dir <- tempdir()

build_approved(approved_pkgs, file = file.path(dir, "approved.rds"))
```

# 4. Update the `logrx.approved` option
Update the `logrx.approved` option to point to your `approved.rds` location. We 
recommend setting this in your `.Rprofile`.

```{r}
options(log.rx.approved = file.path(dir, "approved.rds"))
```

# 5. You're done. Let's axecute! 
`logrx` will take it from there. When each program is executed, packages and 
functions will be compared to `approved.rds` and if any unapproved use is 
found, it will be logged within the "Unapproved Package and Functions" section 
of the log file.

# Example

Let's write a simple script summarizing mean mpg from mtcars. We save this as 
`mpg.R` in the temporary directory `dir` and `axecute()` it.

```{r}
library(dplyr, warn.conflicts = FALSE)

results <- mtcars %>%
   group_by(cyl) %>%
   summarize(mean = mean(mpg)) %>%
   mutate(label = "Mean MPG")

results %>%
   tidyr::pivot_wider(names_from = cyl, values_from = mean, id_cols = label)
```

```{r echo = FALSE}
# write this to the temp directory so we have a script to axecute

text <- 'library(dplyr)

results <- mtcars %>%
   group_by(cyl) %>%
   summarize(mean = mean(mpg)) %>%
   mutate(label = "Mean MPG")

results %>%
   tidyr::pivot_wider(names_from = cyl, values_from = mean, id_cols = label)'
   
fileConn <- file(file.path(dir,"mpg.R"))
writeLines(text, fileConn)
close(fileConn)
```

```{r results='hide'}
axecute(file.path(dir,"mpg.R"), remove_log_object = FALSE)
```

Here we have the log elements for "Used Package and Functions" and "Unapproved 
Package and Functions". We can see we used `library()` from `package:base` and 
`pivot_wider` from `package:tidyr`.  We did not include the base library or 
tidyr functions in our approved list, so this has been logged!

```{r echo=FALSE}
cleaned_log_vec <- c()

cleaned_log_vec <- c(cleaned_log_vec,
                           write_log_header("Used Package and Functions"),
                           write_used_functions())

cleaned_log_vec <- c(cleaned_log_vec,
                           write_log_header("Unapproved Package and Functions"),
                           write_unapproved_functions())
cat(cleaned_log_vec, sep = "\n")
```

```{r cleanup, echo = FALSE}
logrx::log_remove()

unlink(dir, recursive = TRUE)
```
