---
title: "logrx Options"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{logrx Options}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE
)
```

```{r setup}
library(knitr)
library(logrx)
library(tibble)
```

One of the ways that `logrx` has been built to be customizable is to add a set of options to enable different logging and execution elements.

Below are the options and their default values

```{r options_table}
table_ops <- tribble(
   ~option, ~value, ~description,
   "log.rx", "An empty R environment", "Used to store log elements during program exection",
   "log.rx.exec.env", "NULL", "The environment in which the program code is executed",
   "[log.rx.lint]", "library_call_linter()", "A `lintr` object for use in lint checking",
   "[log.rx.approved]", "./approved.rds", "Location of an approved functions file"
)

kable(table_ops)
```

## log.rx.lint

*"lintr provides static code analysis for R. It checks for adherence to a given style, identifying syntax errors and possible semantic issues, then reports them to you so you can take action."*

<br>

Linting can help enforce best practice for a variety of topics including code readability, efficiency, style, consistency, etc.  You can find all available linters [here](https://lintr.r-lib.org/reference/linters.html), or [create your own](https://lintr.r-lib.org/articles/creating_linters.html).

<br>

If you or your organization would like to implement any linters, you can set your `log.rx.lint` option globally so your specific set of checks are run and their results are recorded to your log for every script executed.

<br>

Be default, the `library_call_linter()` is used.  This is to ensure `logrx` will find the correct package and functions used.

<br>

Hester J, Angly F, Hyde R, Chirico M, Ren K, Rosenstock A, Patil I (2022). lintr: A 'Linter' for R Code. <https://github.com/r-lib/lintr>, <https://lintr.r-lib.org>.

## log.rx.approved

See [Logging Unapproved Package and Function Use](approved.html) for additional details.
