---
title: "timber-package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{timber-package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(timber)
```

The purpose of the ```timber``` package is to generate a log upon execution of 
an R script which enables traceability and reproducibility of the executed code. 
The log can be generated according in two ways:

* Using the ```axecute()``` function

* Using the ```log_*()``` functions

# Generating a log using ```axecute()```
```axecute()``` enables the command line submission of a program. A log is 
set-up around the program, and its code is run safely and quitely.
```{r axecute, eval = FALSE}
axecute("my_script.R")
```

# Generating a log using ```log_*()``` functions
Use the ```log_*()``` functions:

* ```log_init()``` to create the environment timber.log

* ```log_config()``` to add the core elements of the log to the environment, and 
 basic elements that are available at the time of configuration

* ```run_safely_n_quietly()``` to execute the program code, and capture errors 
and warnings

* ```log_write()``` to generate and format the log
```{r log_*, eval = FALSE}
log_config("my_script.R")
run_safely_n_quietly("my_script.R")
log_write()
```
