---
title: "Logging for Summary Display Table"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Logging for Summary Disply Table}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(logrx)
```

In this section, we write a script to create a risk-difference table from the 
[PHUSE Test Data Factory ADaM dataset](https://github.com/phuse-org/TestDataFactory), 
using the [`Typlr`](https://atorus-research.github.io/Tplyr/) package. We use 
the `logrx` package to generate a log upon the script execution for 
reproducibility and traceability.

## 1. Load the packages
First, we load the packages that we will use to generate the risk-difference 
table.
```{r}
library(haven)
library(magrittr)
library(Tplyr)
```

## 2. Load the data
Then we load the Adverse Event Analysis Dataset from the 
[PHUSE Test Data Factory ADaM dataset](https://github.com/phuse-org/TestDataFactory). 
The data are stored in a transport file format and we use the 
[`haven`](https://haven.tidyverse.org) package to load them.
```{r}
adae <- read_xpt("adae.xpt")
```

## 3. Build the risk-difference table
Finally, we write a script (`risk_diff.R`) to build the risk-difference table, 
using the [`Typlr`](https://atorus-research.github.io/Tplyr/) package.
```{r results='hide', warning=FALSE}
t <- tplyr_table(adae, TRTA) %>% 
  add_layer(
    group_count(RACE) %>% 
      set_distinct_by(USUBJID) %>% 
      add_risk_diff(
        c("Xanomeline High Dose", "Placebo"),
        c("Xanomeline Low Dose", "Placebo")
      )
  )

build(t)
```

```{r echo = FALSE}
# write this to the temp directory so we have a script to axecute

text <- 't <- tplyr_table(adae, TRTA) %>% 
     add_layer(
       group_count(RACE) %>% 
         set_distinct_by(USUBJID) %>% 
         add_risk_diff(
           c("Xanomeline High Dose", "Placebo"),
           c("Xanomeline Low Dose", "Placebo")
         )
     )

   build(t)'
   
dir <- tempdir()
fileConn <- file(file.path(dir,"risk_diff.R"))
writeLines(text, fileConn)
close(fileConn)

```

## 4. Axecute the script

We will `axecute` the following script.

<iframe width="700" height="400" src='risk_diff_script.html'/>

```{r results='hide', warning=FALSE}
axecute(file.path(dir,"risk_diff.R"))
```

Below is the log. Pay special attention to the Warnings and Result sections.

<iframe width="700" height="400" src='risk_diff_log.html'/>

```{r cleanup, echo = FALSE}
unlink(dir, recursive = TRUE)
```
