---
title: "Logging with tidylog"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using tidylog and logrx}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css, echo=FALSE}
.scroll-100 {
  max-height: 100px;
  overflow-y: auto;
  background-color: inherit;
}
```

In this article, we will create a log with `axecute()` while using the `tidylog` package.  The goal of `{tidylog}` is to provide feedback about `{dplyr}` and `{tidyr}` operations. It provides simple wrapper functions for almost all `{dplyr}` and `{tidyr}` functions, such as `filter`, `mutate`, `select`, `full_join`, and `group_by`. 

## Logging a simple script with {logrx} and {tidylog}

Below we have a simple script using the `us_rent_income` dataset.  We will explore just a few functions avaialbe in `{tidyr}` and `{dplyr}`.  

```{r engine='bash', comment='', echo=FALSE}
cd ..
cd ..
cd data-raw
cat tidylog_ex1.R
```

<iframe width="700" height="400" src='tidylog_ex1.html'/>


## Logging a ADSL script

an  R script that creates and `ADSL` to get a log file.  This file was taken from the `admiral::use_ad_template("adsl")` with a few changes to its contents
to showcase certain features of the `logrx` package's log file.

Users wishing to run a similar script will need to do the following:

* Install the logrx package 
* Copy the below script or use `admiral::use_ad_template("adsl)` to generate it.
* Note this script differs from the template with a call to `diffdf` to do a compare,
a simple custom message is used and results are manipulated for illustrative purposes.  
* Users will also need to make the decision on whether they want to use the Addin of 
`logrx` or use the `aexcute()` directly in a script or in the console to get a log file.

## axecute the adsl.R script

Below is a simple `adsl.R` script generated from the `admiral` package.  Notable features of the script are as follows:

* Calls for getting SDTM datasets, e.g. `DM`, `EX`, `DS`
* Converting SAS blanks to NAs 
* Typical derivations you would need to get treatment groups, start/end dates, duration
* Typical derivation for Screen Failures, Screen Flags, Death Flags
* Creating numeric variables with custom format functions
* A call to  `diffdf::diffdf()` to do a simple compare between two datasets
   * Note: The compare will create a warning that the two objects being compared have different columns.  This warning will appear in the log
* Simple message inserted for illustration.  This message will appear in the log.
* Manipulated results that will appear in the log file.

### Inspect adsl.R script

Feel free to explore the script.  The next section showcases the output for log file for the 
this script.

<iframe width="700" height="400" src='adsl_script.html'/>

<br>

**NOTE:**  Users can do the following to axecute their script:

1.  Use the Addin
2.  Use `logrx::axecute("file.R")` directly in their script [See Vignette TODO]
3.  Use `logrx::axecute("file.R")` in the console
4.  Use `logrx::axecute("file.R")` in a batch script [See Vignette TODO]


## Log Output adsl.R

1. logrx Metadata and User and File Information, of the log contains information about the version of logrx used to create this log as well as user and file information.
2. Session Information, Packages , External software, Masked Functions, Used Package and Functions and Program Run Time Information of the log file contains information for everything used to run the R script.  We believe this information suffices to re-create the environment needed for re-running the script.
3. Errors and Warnings and Messages, Output, and Result are the final sections of the log file.  Please note the following
   * Warning from the comparison file.
   * Message sent from the script to the log file
   * Results appended to the file

<iframe width="700" height="400" src='adsl_tidylog.html'/>


